SST_patterns

### 2020-01-20 SST_patterns.Rmd
merge

ggplot(data = Combined_frequency, aes(x = t, y = number_of_signals)) +
  geom_line(aes(colour = distance)) +
  geom_point(aes(colour = distance)) +
  geom_smooth(aes(colour = distance), method = "lm") +
  facet_wrap(~site)+
  theme(axis.text.x = element_text(angle = 90, hjust =1, vjust = 0.5))

####

>>>>

ggplot(data = Combined_frequency, aes(x = t, y = number_of_signals)) +
  geom_line(aes(colour = distance)) +
  geom_point(aes(colour = distance)) +
  geom_smooth(aes(colour = distance), method = "lm") +
  facet_wrap(~site)+
  theme(axis.text.x = element_text(angle = 90, hjust =1, vjust = 0.5))
####
